Presentation Proposal for Three Neat Tricks in Coq 8.5

### 2020-07-30 papers/source/fiat-crypto/pldi-2018/response.md

Thanks for the wealth of suggestions on improving the paper's presentation.  We'll be glad to consider reordering material or adding new information.  For now, we'd like to point out how a few of the requests for expansion can be addressed with existing material in the paper, possibly in the context of some brief new clarifications.

- Review A asks for more detailed comparison with other approaches.  First, on the side of performance of related code, competing approaches involve writing code by hand, and they generally copy quite faithfully from the best known implementations (e.g., OpenSSL), so our comparison with best-known versions is a strong proxy for the performance elements of HACL*, Jasmin, and Vale.  On the side of developer effort, we hope the message came across that, once a new algorithm is implemented in our framework, it becomes almost free to recompile for a new prime modulus or a new hardware-architecture class, while as far as we know, no high-performance past project had implemented/verified more than one configuration of that kind per algorithm.  Furthermore, we don't know of any prior high-performance verification of NISTP256 or Montgomery reduction, which are used by the vast majority of TLS connections today.
- Review B asks how developers use the tool and what comes out in the end.  We should perhaps have been clearer that our story involves at least three layers: the framework, generic implementations of algorithms, and instantiations of those algorithms to new parameters.  Targeting a new algorithm involves new coding and proving work (often nontrivial).  However, compiling an existing algorithm with new parameters really does only require the level of effort seen in the "Input" part of Figure 1 (no proving, etc.).  Much of the PLDI audience probably takes that sort of thing for granted, but as far as we know, all past approaches have required days of work to "recompile" an existing algorithm for new parameters.  And, yes, the "Output" part of Figure 1 is representative of what our tool produces.  It can be copied-and-pasted into a project, compiled and linked as a library, etc.
- Review C expresses skepticism that crypto-library authors will use this tool.  We're not sure what to say beyond our original (blinded) description of how one of the most used crypto libraries has already adopted our framework (and more has happened since paper submission).  It seems there is a nontrivial segment of the crypto world where stronger security guarantees can outweigh the last 10% of performance.
- Review D says that we failed to discuss side-channel resistance, though we believe the issue was treated fully (but perhaps the presentation deserves rearranging).  In addition to several other mentions throughout the paper, see the paragraph starting on line 951.  Essentially, our target language only exposes instructions that preserve constant time.
- Review D asks how the compiler chooses a representation.  The main part of our framework is designed to take the representation as a parameter, and it is hard to predict analytically which choice will perform best.  Thus, the experiments of Figure 3 involve heuristic generation of several representations per configuration (prime modulus and hardware target), compiling with each choice, and keeping the best-performing version.  Currently we only bother generating 2 representations per configuration, but it is easy to add new heuristics to the mix, with no new formal-methods work.
- Review E asks who performs CPS translation and makes important design choices.  Currently the programmer implementing a new generic algorithm codes and proves a CPS version manually.  We would like to apply CPS translation automatically, though our initial efforts were flummoxed by the dependent types used by our direct-style algorithms.  Design choices like data-representation changes for points are also made manually by the programmer implementing a new algorithm.  From this question and parts of other reviews, we see that one point we failed to make clearly is that nontrivial manual work goes into implementing a new verified, generic algorithm, while we then provide a good automation story for instantiating that algorithm with new parameters.

More responses past the 700-word limit
======================================

We see two main use cases for the artifact produced in this work.
First it can be used in a plug-and-play fashion to generate modular arithmetic code using the already-implemented strategies.
This use case is rather narrow but very expedient when it is applicable.
More importantly, we think there is a lot going for implementing new optimized algorithms in the style we propose.
In particular, the code reuse made possible by our library (relying on a predictable specializing compiler) allows new operations (e.g. polynomial multiplication) and tricks (e.g. Karatsuba's multiplication, interleaved carrying and reduction) to be added with less effort than using any other methodology we are aware of.
For example, we implemented (and proved correct) Goldilocks Karatsuba multiplication at a conference lunch break when the author of the technique inquired whether our framework could support it.

Review D
--------

We wholly agree that going from the C code our pipeline generates to speed-record-setting assembly code requires a whole new set of techniques in addition to those described in this paper.
In our opinion, our output language is a natural interface between domain-specific and microarchitecture-specific optimizations, so that the C-to-assembly translation would not need to understand modular arithmetic or limbed representations to produce the best assembly we know to wish for.
As the first reviewer points out, a simple translation validation should be sufficient to connect the assembly code that includes low-level optimizations to the output of our pipeline it was generated from.
In fact, as seen in libsecp256k-c64, it is even possible to improve on our performance within the C language by munging source code (at the same abstraction layer as our generated code) into a form that happens to persuade a particular compiler to produce the desired register allocation and instruction schedule.

Asymmetric cryptography implementations (ours and others') use very simple CPU instructions and cannot benefit from the AES/SHA implementations found on some popular CPUs.

We view producing straight-line code as a strength rather than a limitation.
Any conventional compiler (e.g., gcc, ocamlc) could turn code roughly at the same abstraction layer as our templates into machine code that uses loops and branches, but so far it has taken significant amounts of (duplicative) human effort to produce specialized constant-time code.
We do not generate loops or complicated control-flow logic (e.g., as seen in elliptic-curve scalar multiplication routines that use precomputed tables) because writing (and verifying) the code with loops in the first place is pleasant and reliable when compared to doing the same for specialized field-arithmetic implementations.
Our library already includes verified code with iteration and conditionals, and we have integrated it (with proofs) with our generated field arithmetic.
There is just nothing novel about it.

Review E
--------

The question "In Section 2.3, are we assuming $p < 2^{64}$?" may have been caused by our typo of $\mathbb N_p$ in place of plain $\mathbb N$ on line 333.  Sorry!

On guarantees throughout our pipline: each run of the entire pipeline, from a specification like "a * b mod m" to C code, generates a proof certificate for functional correctness.
For the early phases, the proof is generated anew using tactics on each execution.
The flattening and word-size-selection transformations (the "certified compiler") are proven correct once and for all, and this proof is appropriately linked into the end-to-end proof.

The hand-modified version in section 6.2 is proven equivalent to the generated code it replaces before word-size selection using the `ring` tactic from Coq's standard library.
It is indeed ad-hoc but has an end-to-end Coq-checkable correctness proof against the same specification as the rest of the library, and the proof is very automated, in the tradition of translation validation.
We also intended that manual transformation as an experiment to zero in on the nature of our performance gap with other code; we are not suggesting manual code tweaking as part of the intended usage of a future, improved version of our framework (and it is easily skipped now if being within 10% of best-known performance is acceptable).

### 2020-07-30 papers/source/fiat-crypto/popl-2018/response.md

We're very glad to have reviews from 3 experts!
The comments point out some perspective issues that we're eager to address by revising the paper.
We'll mention those before returning to answer some more specific questions, after the 600-word limit.

Most importanly, we want to emphasize what we see as the main novelty of the paper: encapsulation of intricate machine arithmetic and its proofs in libraries, so that not only is there no significant manual proof effort for each new prime modulus; we don't even need to do something like call an SMT solver to prove each new suite of code.  Rather, we have proved the whole family of algorithms correct once and for all, in a way that still lets us generate pretty fast, idiomatic low-level code.

Next, there's a perspective summed up well in Reviewer C's comment that other recent work seems "much ahead [of us] in terms of the state-of-the-art of verified cryptography."
However, none of that work presents higher-level abstractions like we called out in the prior response paragraph.
We tried to sketch out our bigger-picture plan in the paper, where we do plan to connect to proofs of cryptographic security, of constant-time execution, and with a trusted base that ends in assembly language.
Those connections have not been made yet, but we felt that our main novelty (described in the prior response paragraph) is valuable and interesting enough on its own.

We appreciate the pointers to 3 papers (on HACL*, Jasmin, and Vale) that weren't published as of the POPL deadline.
As far as we know, none of those demonstrate almost-complete code or proof reuse across prime moduli for machine arithmetic, as we do.
(We should point out that the mainstream assembly-generating scripts that the Vale paper mentions are operating at a much lower level of abstraction than for our work, not coming close to abstracting out a prime modulus.)
However, as the reviewers point out, those other projects include complementary parts of a verification stack, so we plan to look into ways to connect to these systems, rather than building our own alternatives.
For instance, our pipeline is a perfect match with Jasmin: the final terms that we produce are effectively in a subset of the Jasmin input language.
We aren't aware of any duplication of functionality between our respective tools: every one of our phases is needed to produce code low-level enough for Jasmin or Vale to accept as input.

It seems worth reiterating that generation of C code is just an element of our current experimental setup: our formal development actually bottoms out in a simple straightline-code language (with a subset of the features of Jasmin), and we do not intend to use C in any way in the extensions we sketch as important future work.

Finally, multiple reviewers commented on the amount of space we spend in the paper on reviewing material well-known to experts on ECC.
We tried to negotiate the balance between keeping those experts interested and keeping a general POPL audience engaged; we will think about tweaking the balance based on the reviewers' remarks.
However, we do think that our presentation of key strategies often includes ideas that are "obvious in retrospect," but that were not known in this form to crypto experts.
Formulating the ideas in this way was crucial to making our Coq proofs tractable.
One example is the question we consider in Section 4.3, on flexible representation of multi-digit numbers.

# Further detailed responses (past word limit)

## How to prove equivalence between our initial generated version of a routine and another version where we have done some optimizations manually?

With straightline low-level code like is involved here, we just need to evaluate the two versions as functional programs and use Coq's `ring` tactic to prove equivalence of results.
In other words, naive symbolic execution suffices.

## Avoiding timing side channels

By design, our output AST type can *only* represent constant-time code; there are no branches, loops, or divisions.
(We do assume that the processor actually implements these instructions in a constant-time fashion, but checking that must be done experimentally as long as we do not have access to a precise specification or implementation that captures this timing behavior.)
We only mention timing analysis as part of future work that would extend our derivation pipeline to higher-level cryptographic code.

## Where is the generated code in the supplementary material?

The generated code is in `src/Specific/NISTP256/AMD64/` and `src/Specific/X25519/C64/`; to see output in our AST format, look at the files ending in `.log`.
To see C, run `make c` to generate `.c` files.

## fsatz: can we deal with 1/(1/x)?

Yes, and it is not a special case for the algorithm.
`src/Algebra/Field_test.v` contains several more complicated examples; adding `Lemma inv_inv x (H:x <> 0) : 1/(1/x) = x. fsatz. Qed.` passes.

## Effort to choose good carrying strategies

Selecting a carry chain is a complex problem; choices depend heavily on the target architecture, and there is not really a good way to evaluate them other than empirical testing.
Some general heuristics exist but may not provide optimal choices.
However, we could easily integrate any heuristic into our build process, with no effect on proofs.

## Meaning of "Our initial implementation, misguided by types, ..."

We are referring to a classic sort of mistake when programming with dependent types: calling it a day when a routine type-checks, even before it has been proven correct.
We were lulled into a false sense of security by the width-tracking dependent types of bitvectors, in a tricky loop with a surprising design space that the crypto literature hadn't spelled out.

## Extending our results to cover signatures and cyphers, not just lower-level ECC operations

Actually, we have composed the operations into more complex schemes (ed25519) in Gallina, but we haven't formalized extracting C function calls because we eventually plan to cut out C and output straight to assembly.
Still, we used our generated field-arithmetic code as subroutines in complete Gallina (Coq) programs for signing and signature verification, which we proved equivalent to their simple specifications.
So carrying out this exercise ensures that we chose the right formal interface for the code that makes up the main novelty of our project.
(We mention this aspect in the paragraph with line 397.)

## New work that needs to be done for each new curve

For each new *point format*, it is necessary to write a new correctness proof, although the proof would almost certainly be a single invocation of `fsatz`.
The library already includes code and equivalence proofs for affine, XYZT, and Niels variants of Edwards coordiantes; affine, Jacobian, and Projective Weierstrass coordinates; and affine and XZ Montgomery coordinates.
When reusing an existing point format for a new curve or a new hardware architecture for an existing curve, the new implementation work is roughly just in the configuration snippets shown near the beginning of our Experimental Results section.

## Why not implement and benchmark more operations than just for 25519 and P256?

P256 and X25519 make up the vast majority of ECC usage on the Internet.
For example TLS ECDHE was measured to be 97% P256 in 2015[1]; since then X25519 has been deployed, reaching around 30% of connections established by Google Chrome.
We find it much more valuable to increase the depth of our verification (we already use higher-level specs than in any other work we know of, but there is still room to extend towards assembly) and performance of the code (fixing up the low-level inefficiencies pointed out by the reviewers and ourselves) than work on less commonly used curves.
If we wanted to further demonstrate the flexibility of the framework, it would be more meaningful to create different implementations of X25519 and P256, because that is where the performance engineering research is focused.
We could, of course, use the existing library to generate code for other curves (e.g. P384), but since we (and most libraries we know) would not prioritize their performance, the benchmarks would be less revealing.
Once we have a functioning pipeline to assembly code, we might seek to imitate the x25519-amd64-64 implementation that is fastest in our benchmarks but awkward to represent as C code.
However, since we intentionally chose our implementation strategies for X25519 and P256 to be as different as possible, every technique we know for implementing these curves (or any curves at a similar security level) would be an interpolation between the tricks used in our saturated-Montgomery-multiplication P256 code and unsaturated-Solinas-reduction X25519 code (e.g. x25519-amd64-64 uses saturated arithmetic with Solinas reduction).
New optimizations like specialized Karatsuba multiplication used for Goldilocks primes (e.g. X448) would need to be added and proven once as high-level optimizations, but again, we see expanding the work in other ways as more practically valuable at this moment.

[1]: "TLS in the wild: An Internet-wide analysis of TLS-based protocols for electronic communication" https://www.net.in.tum.de/fileadmin/bibtex/publications/papers/2016-tls-ndss.pdf

## Explanation of local-variable bitwidth inference

Sorry for the possibly cryptic description "abstract interpretation with intervals"!
We do think that (with the exception of bitwise operators and their sometimes-not-obvious conservative rules) we follow the abstract-interpretation literature pretty closely, even avoiding the complexities of code with interesting control flow, since we only analyze straightline code.
Here's another try at a summary: the analysis starts with some lower and upper bound for each variable, and applies sound (but not necessarily complete) operation-specific rules to derive bounds for further variables defined in the program, computing each's bound as a simple function of bounds for its operands.
Each variable is assigned the fastest integer type that encompasses its full computed interval.
This transformation and analysis is proven to preserve the output value for all code.

### 2021-08-15 papers/source/lob-paper/review-responses.md

Thank you all for the feedback; we really appreciate it.

It's now clear that one of the most subtle parts of Lӧb's theorem is distinguishing between semantics, syntax, quoted syntax, and doubly-quoted syntax, and that our paper does not make it easy enough to make these distinctions; we will edit the paper to do far more hand-holding here, and will drop the cute notations that blur this distinction.  The points about cute notations and magic tricks, and about consistently using the same words for the same concepts, are well-taken, and we will fix these things.

The suggestion to begin with the Y combinator is a good one; thank you reviewers B and C!

We now realize that the traditional presentation of Curry-Howard is classical and identifies provability with truth; to extend it neatly to talking about provability logic in a computational manner, we've presented it in from within the lens of Brouwer’s intuitionism; we will clarify our use of the word "truth".

Reviewer-specific responses, followed by an appendix of reviewer-specific responses that didn't fit in the first 500 words.

========================

Reviewer A:
------------------------

Indeed, it seems impossible at first glance to prove Lӧb's theorem without some sort of `QUINE` primitive.  But it turns out it is possible!  Section 10 sketches how to do this, and we flesh it out for those interested in the supplemental material.

Your point about cute names is well-taken, and the use of capitalization to distinguish the syntax for types from the syntax for terms, and using names rather than symbols to distinguish syntax from semantics, are both great ideas.

========================

Reviewer B:
------------------------

- The Y combinator is unsound in a proof assistant; non-termination leads to proofs of false.  Indeed, Lӧb's theorem is nothing but a variant of the Y combinator with (un)quoting, *which implicitly forbids infinite loops*.  We will make clear that this paper is implementing this variant of the Y combinator in varying degrees of detail, in a way that is terminating-by-construction.

- The type `□ (‘□’ X ‘→’ X) → □ X` corresponds to the deduction rule "from `⊢ □ X → X`, we deduce `⊢ X`".  An alternative would be "`⊢ □ (□ X → X) → □ X`".

========================

Reviewer C:
------------------------

If we understand correctly, you want to see us separate the proof of Lӧb's theorem from its semantics, using a variant of S4.

This is a good idea, and we may replace the section that assumes a quine with this formalization (see the appendix to this note for a 40 line version).

- We assumed that for those unfamiliar with encodings of type theory in type theory, working with strings and string replacement and quotation in Python would be more familiar than working with quotation and substitution on abstract syntax trees.  We acknowledge that it might be clearer to present the quotation operation from scratch, rather than relying on intuition from Python.  (Note that internally implementing quotation on well-typed syntax trees is, as far as we are aware, still an open problem, implementation-wise.)

========================
Appendix
========================

========================

Reviewer A:
------------------------

I'm a bit confused by your second bit of code; the type of `LÖB` should be `EXP → EXP`, and `löb` should have type

```
löb : {T : TYP} {interp : EXP} → interp ∶ (ARR (BOX T) T) → (LÖB interp ∶ T)
```

Your hole can be filled with `Σ EXP (λ e → e ∶ T)`, and the denotation function for `EXP` is the same as in your first block of code.

What you are doing here, I think, is separating raw terms from their typing judgments.  What we do is remove the `LÖB` primitive and reimplement it using a `QUINE` primitive, and then sketch how that can be removed entirely.

We'd be curious to see these references in the context of quantum computation; I've not seen any physical interpretation of the modal □ operator.

========================

Reviewer B:
------------------------

- The proof of Lӧb's theorem uses self-reference in an essential way; it results from analyzing the self-referential sentence "If this sentence is provable, then A".  We explain that this is used to prove Lӧb's theorem in the second-to-last paragraph in the introduction, containing "This, in a nutshell, is Löb’s theorem."  We'd very much appreciate suggestions on what made this unclear.

- Thank you for the suggestions about unifying the synonyms and clarifying types where they are not obvious; we'll do this.

- The relation between the program `Lob(X)` on page 2 and `□(□A → A) → □A` is that `Lob(X)` is the key ingredient of the proof of Löb’s theorem; it is the type corresponding to the sentence "If this sentence is provable, then A" which is mentioned above.

- Interpreting `□A` as `1 → A` does not fix the termination problem.  It is possible to have a total language with a Löbian combinator `(□A → A) → A` if we interpret `□A` as syntax, but if we interpret it as `1 → A`, we get `((1 → A) → A) → A`, which is just the Y combinator.  Said another way, `1 → A` suspends computation at *runtime*, but to make Lӧb's theorem work, we must suspend computation at *compile-time*.

- Regarding `repr`, we can *add* a level of quotation to anything that's already quoted.  We plan to make it easier to see at a glance the distinction between semantics, (singly-quoted) syntax, and (doubly) quoted syntax.

- Regarding "There is no syntactic proof of absurdity", we again need to make clearer the distinction between syntax and semantics.  Agda has no proof of absurdity.  If we build our syntax in a stupid way, we might permit a syntactic proof of absurdity in the object language (which is not the full extent of Agda, and which we have no guarantee is identical to a subset of Agda); we must prove that it is impossible to derive contradictions in our object language.

- Regarding the footnote, `□(□X → X) → □X` is a valid expression of the type of Lӧb's theorem, but it's not a valid type for a constructor of an inductive datatype `□`, again for termination (positivity) reasons.

- Thank you for the feedback on the Prisoner's dilemma section; we will add a bit more exposition to make it more self-contained.

- Agda does not have a notion of truth distinct from provability; this is what we meant by "banish [the word] 'truth'".  We will add more hand-holding here; the reason to talk about "provability" is that it is extremely confusing to say "P is false, and 'P is false' is false" while it is only mildly confusing to say "we can prove that P is absurd, but we can also prove that proving "WE CAN PROVE THAT P IS ABSURD" is absurd".

========================

Reviewer C:
------------------------

The formalization and semantics of S4, specializing the quine/fixed-point theorem to the Lӧbian sentence.  We may use this to replace the formalization based on the Quine primitive (obviously with added explanation of the Lӧb′s-Theorem proof term).

```
data TYP : Set where
  ARR : TYP → TYP → TYP -- the type of implications, or function types
  BOX : TYP → TYP -- the modal □ operator, denoted to TERM
  LӦB-SENTENCE : TYP → TYP -- the Lӧbian sentence "If this sentence is provable, then A"
                           -- this is the modal fixpoint of λ Ψ. □ Ψ → A

data TERM : TYP → Set where
  nec : {A : TYP} → TERM A → TERM (BOX A)                                             -- from A, we deduce □ A
  distr : {A B : TYP} → TERM (ARR (BOX (ARR A B)) (ARR (BOX A) (BOX B)))              -- we deduce □ (A → B) → □ A → □ B
  s4 : {A : TYP} → TERM (ARR (BOX A) (BOX (BOX A)))                                   -- we deduce □ A →  □ □ A
  app : {A B : TYP} → TERM (ARR A B) → TERM A → TERM B                                -- from A → B, and A, we deduce B
  lӧb→ : {A : TYP} → TERM (ARR (LӦB-SENTENCE A) (ARR (BOX (LӦB-SENTENCE A)) A))       -- LӦB-SENTENCE A is Ψ such that Ψ → (□ Ψ → A)
  lӧb← : {A : TYP} → TERM (ARR (ARR (BOX (LӦB-SENTENCE A)) A) (LӦB-SENTENCE A))       -- LӦB-SENTENCE A is Ψ such that (□ Ψ → A) → Ψ
  compose : {A B C : TYP} → TERM (ARR A B) → TERM (ARR B C) → TERM (ARR A C)          -- from A → B and B → C, we deduce A → C
  compose2 : {A B C : TYP} → TERM (ARR A B) → TERM (ARR A (ARR B C)) → TERM (ARR A C) -- from A → B and A → B → C, we deduce A → C

Lӧb′s-Theorem : {A : TYP} → TERM (ARR (BOX A) A) → TERM A -- from □ A → A, we deduce A
Lӧb′s-Theorem {A} refl-rule = app prog (nec (app lӧb← prog))
  where prog : TERM (ARR (BOX (LӦB-SENTENCE A)) A)
        prog = compose (compose2 s4 (compose (app distr (nec lӧb→)) distr)) refl-rule

⟦_⟧ᵀ : TYP → Set
⟦ ARR A B ⟧ᵀ = ⟦ A ⟧ᵀ → ⟦ B ⟧ᵀ
⟦ BOX T ⟧ᵀ = TERM T
⟦ LӦB-SENTENCE A ⟧ᵀ = TERM (LӦB-SENTENCE A) → ⟦ A ⟧ᵀ

⟦_⟧ᵗ : {T : TYP} → TERM T → ⟦ T ⟧ᵀ
⟦ nec e ⟧ᵗ = e
⟦ distr ⟧ᵗ box-a-b box-a = app box-a-b box-a
⟦ s4 ⟧ᵗ = nec
⟦ app f x ⟧ᵗ = ⟦ f ⟧ᵗ ⟦ x ⟧ᵗ
⟦ lӧb→ ⟧ᵗ = λ x → x -- this implication is true because on denotation, the two are judgmentally equal
⟦ lӧb← ⟧ᵗ = λ x → x -- this implication is true because on denotation, the two are judgmentally equal
⟦ compose f g ⟧ᵗ = λ x → ⟦ g ⟧ᵗ (⟦ f ⟧ᵗ x)
⟦ compose2 f g ⟧ᵗ = λ x → ⟦ g ⟧ᵗ x (⟦ f ⟧ᵗ x)
```

- Section 3 is intended to be a crash course in formalizing the syntax and semantics of type theory for those who have not seen it before.  Perhaps your point is that it does not provide enough explanation for those unfamiliar with it, that it is (intentionally) irrelevant for those familiar with formalizing type theory in type theory, and that what little content in the section falls into neither category should be merged into the other sections, to improve flow.  This is a good point.

### 2021-08-15 presentations/coq-workshop-2014/coq-workshop-proposal-tactics-in-terms.tex
Add more deploy

\usepackage{amsmath,amssymb}
\usepackage[utf8]{inputenc}
% copy-pastable ligatures
\input{glyphtounicode}
\pdfgentounicode=1
\usepackage[margin=1in]{geometry}
\usepackage{verbatim}
\usepackage{comment}
\usepackage{xcolor}
\usepackage{fancyhdr}
\title{Presentation of Three Neat Tricks in Coq 8.5}
\author{Jason Gross}
\date{ITP 2014: 6th Coq Workshop}
\usepackage[pdftex,
            pdfauthor={Jason Gross},
            pdftitle={Presentation of Three Neat Tricks in Coq 8.5},
            pdfsubject={ITP 2014: 6th Coq Workshop},
            pdfkeywords={Coq 8.5, Ltac, Gallina, binders, notations, tactics, recursion, recursive tactics, typeclasses, universe polymorphism, universes}]{hyperref}
\chead{Presentation of Three Neat Tricks in Coq 8.5 \\ Jason Gross \\ ITP 2014: 6th Coq Workshop}
\thispagestyle{fancy}
% Keywords:
% Coq 8.5
% Ltac
% Gallina
% binders
% notations
% tactics
% recursion
% recursive tactics
% typeclasses
% universe polymorphism
% universes

>>>>

\usepackage{amsmath,amssymb}
\usepackage[utf8]{inputenc}
% copy-pastable ligatures
\input{glyphtounicode}
\pdfgentounicode=1
\usepackage[margin=1in]{geometry}
\usepackage{verbatim}
\usepackage{comment}
\usepackage{xcolor}
\usepackage{fancyhdr}
\title{Presentation Proposal for Three Neat Tricks in Coq 8.5}
\author{Jason Gross}
\date{ITP 2014: 6th Coq Workshop}
\usepackage[pdftex,
            pdfauthor={Jason Gross},
            pdftitle={Presentation of Three Neat Tricks in Coq 8.5},
            pdfsubject={ITP 2014: 6th Coq Workshop},
            pdfkeywords={Coq 8.5, Ltac, Gallina, binders, notations, tactics, recursion, recursive tactics, typeclasses, universe polymorphism, universes}]{hyperref}
\chead{Presentation Proposal for Three Neat Tricks in Coq 8.5 \\ Jason Gross \\ ITP 2014: 6th Coq Workshop}
\thispagestyle{fancy}
% Keywords:
% Coq 8.5
% Ltac
% Gallina
% binders
% notations
% tactics
% recursion
% recursive tactics
% typeclasses
% universe polymorphism
% universes
